### 2021-08-12 README.Rmd
Revised ctrlfiletemplate and datafiletemplate. No EWN
added getprojyrC and plothsstats. No EWN

* 2021_07-28 aMSE 0.0.0.800 Added functions (changecolumn, getrecdevcolumn, gettasdevssq) to assist in automated operating model conditioning on the fishery. Also modified the biology_plots and oneyear and oneyearcat to assist with speeding the processes. Lots of additional minor changes but some important ones to do_MSE (read the help, ?do_MSE).

* 2021-07-20 aMSE 0.0.0.900 Added do_condition and compareCPUE. Both used to speed the conditioning of the operating model, though a number of developments are still under development. Currently can automatically search for the AvRec value that will optimize the sum-of-squared residual fit between the
observed CPUE in the historical period, and those predicted by the conditioned model. The undeveloped bit related to the ad hoc recruitment deviates.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# OBVIOUSLY you should modify the rundir and datadir to suit your own computer
if (dir.exists("c:/Users/User/DropBox")) {
  ddir <- "c:/Users/User/DropBox/A_codeUse/aMSEUse/scenarios/"
} else {
  ddir <- "c:/Users/Malcolm/DropBox/A_codeUse/aMSEUse/scenarios/"
}
doproject <- TRUE  # change to FALSE if only conditioning is required
verbose <- TRUE
postdir <- "testnew"  # also used to label the output HTML file 
rundir <- paste0(ddir,postdir)
datadir <- paste0(ddir,"tasdata")
alldirExists(rundir,datadir,verbose=verbose)
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a zone.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example control and data files in the DropBox folder:
# C:\Users\User\Dropbox\National abalone MSE\aMSE_files. Copy the control2.csv
# and zonewest.csv into you rundir. Then, assuming yo have the very latest
# version of aMSE = 5300, the following code should work. Recently both aMSE and
# makehtml have been altered so that all references to resdir have been changed
# to rundir, so both packages will need updating. See their respective GitHub
# readme pages for details.

# HarvestStrategy.R should be in datadir, if it is to be shared by scenarios
source(paste0(datadir,"/TasmanianHS.R"))
# run the scenario --------------------- Obviously unhash this to make it work
# out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,hcrfun=mcdahcr,
#                  sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#                  getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=50,
#                  cleanslate=TRUE,verbose=TRUE,doproject=doproject,ndiagprojs=4,
#                  openfile=TRUE,savesauout=FALSE)
# make results webpage ---------------------------------------------------------
# replist <- list(starttime=as.character(out$starttime),
#                 endtime=as.character(out$projtime))
# glb <- out$glb
# projy <- ifelse(doproject,glb$pyrs,0)
# runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
#                    "  replicates = ",glb$reps,",   years projected = ",projy,
#                    "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
#                    "  Randomseed for conditioning = ",out$ctrl$randseed)
# 
# make_html(replist = replist,  rundir = rundir,  width = 500,  openfile = TRUE,
#           runnotes = runnotes,   verbose = FALSE,  packagename = "aMSE",
#           htmlname = postdir)

>>>>

* 2021-08-12 aMSE 0.0.0.500 Modified do_MSE and added plothsstats, streamlined the conditioning. No EWN.

* 2021-08-02 aMSE 0.0.0.700 Revised the 'ctrlfiletemplate' and 'datafiletemplate' functions to reflect the new usage. It should now be possible to run an example scenario related to M15h75.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
options("show.signif.stars"=FALSE,
        "stringsAsFactors"=FALSE,
        "max.print"=50000,
        "width"=240)
# declare libraries ------------------------------------------------------------
library(aMSE)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the rundir and datadir to suit your own setup
prefixdir <- "C:/A_Mal/scenarios/"
verbose <- TRUE
postfixdir <- "M15h75"
rundir <- paste0(prefixdir,postfixdir)
datadir <- rundir
alldirExists(rundir,datadir,verbose=verbose)
controlfile <- "controlM15h75.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a saudata.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example files in the DropBox folder:
# .\..\Dropbox\National abalone MSE\aMSE_files\scenarios\examplerun. Read the 
# 'Using_aMSE' section in the Documentation .docx file in the documentation 
# directry  Then, assuming you have the very latest version of aMSE = 500, 
# the code in the documentation file (or in the 'run_aMSE.R' file within the
# examplerun subdirectory should work.

# HarvestStrategy.R should also be in rundir
source(paste0(rundir,"/TasmanianHS.R"))
# run the scenario --------------------- Obviously unhash this to make it work
#
# out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,hcrfun=mcdahcr,
#               sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#               getdata=tasdata,calcpopC=calcexpectpopC,makeouthcr=makeouthcr,
#               varyrs=7,startyr=48,cleanslate=TRUE,verbose=TRUE,
#               ndiagprojs=4,savesauout=TRUE)
# 
# makeoutput(out,rundir,datadir,postfixdir,controlfile,openfile=TRUE,verbose=FALSE)
